---
output:
  rmarkdown::github_document:
    html_preview: no
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

```{r, include = FALSE}
devtools::load_all()
```

# rscip: Interface to SCIP
<!-- badges: start -->
[![lifecycle](https://img.shields.io/badge/Lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![R-CMD-check-Ubuntu](https://img.shields.io/github/actions/workflow/status/jeffreyhanson/rscip/R-CMD-check-ubuntu.yaml?branch=master&label=Ubuntu)](https://github.com/jeffreyhanson/rscip/actions)
[![R-CMD-check-Windows](https://img.shields.io/github/actions/workflow/status/jeffreyhanson/rscip/R-CMD-check-windows.yaml?branch=master&label=Windows)](https://github.com/jeffreyhanson/rscip/actions)
[![R-CMD-check-macOS](https://img.shields.io/github/actions/workflow/status/jeffreyhanson/rscip/R-CMD-check-macos.yaml?branch=master&label=macOS)](https://github.com/jeffreyhanson/rscip/actions)
[![R-CMD-check-fedora](https://img.shields.io/github/actions/workflow/status/jeffreyhanson/rscip/R-CMD-check-fedora.yaml?branch=master&label=Fedora)](https://github.com/jeffreyhanson/rscip/actions)
[![Documentation](https://img.shields.io/github/actions/workflow/status/jeffreyhanson/rscip/documentation.yaml?branch=master&label=Documentation)](https://github.com/jeffreyhanson/rscip/actions)
[![Coverage Status](https://img.shields.io/codecov/c/github/jeffreyhanson/rscip?label=Coverage)](https://app.codecov.io/gh/jeffreyhanson/rscip/branch/master)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/rscip)](https://CRAN.R-project.org/package=rscip)

<!-- badges: end -->

The _rscip_ package provides an interface to the [_SCIP_ (Solving Constraint Integer Programs)](https://www.scipopt.org/) solver. Specifically, _SCIP_ is an open-source optimization solver that can solve mixed integer programming (MILP) problems. By interfacing with the _SCIP_ solver, the _rscip_ package can be used to generate optimal solutions to optimization problems. Although _SCIP_ can also solve mixed integer non-linear programming (MINLP) problems, this functionality is not provided by the _rscip_ package.

## Installation

The package is not available on [The Comprehensive R Archive Network](https://cran.r-project.org/). To install this package, please use the following _R_ code to install it from the [source code repository on GitHub](https://github.com/jeffreyhanson/rscip).

```{r, eval = FALSE}
if (!require(remotes)) install.packages("remotes")
remotes::install_github("jeffreyhanson/rscip")
```

## Usage

Here we will provide a brief example showing how the package can be used to solve an optimization problem.

```{r}
# load package
library(rscip)

# define optimization problem and solve it
#' # Mathematically define a mixed integer programming problem
#' ## maximize:
#' ##   1 * x + 2 * y + 0.5 * z
#' ## subject to:
#' ##   x + y <= 1
#' ##   3 * x + 4 * z >= 5
#' ##   z = 4
#' ##  x <= 10
#' ##  y <= 11
#' ##  z <= 13
#' ##  x, y, z is integer
result <- scip_solve(
  obj = c(1, 2, 0.5),
  lb = c(0, 0, 0),
  ub = c(10, 11, 13),
  vtype = c("I", "I", "I"),
  A = matrix(c(1, 1, 0, 3, 0, 4, 0, 0, 1), byrow = TRUE, nrow = 3),
  sense = c("<=", ">=", "="),
  rhs = c(1, 5, 4),
  modelsense = "max"
)

# print solution values
print(result$x)

# print objective value
print(result$objval)

# print solver status
print(result$status)
```

## Citation

Please cite the [_SCIP_ solver](https://www.scipopt.org/) when using this _R_ package in publications.

```{r, echo  = FALSE, result = "asis", comment = ""}
citation("rscip")
```
